\documentclass[10pt]{letter}

\input{cv_structure.tex}

\addtolength{\medskipamount}{-1\medskipamount}

\signature{Elliot Marsden}

\begin{document}

    \begin{letter}{}

        I'm currently finishing writing my thesis towards a \smaller{PhD} in computational Biophysics in the Physics department of Edinburgh University. Before then I graduated from Durham University, where I studied Theoretical Physics. My \smaller{PhD} has consisted mainly of analysing the movement of large numbers of bacteria in confining environments, through numerical simulations, and statistical analysis of experimental data.

        The simulations and analysis were carried out mainly in Python, with numerically intensive parts written in C. Analysing the positions of thousands of bacteria over time involved filtering and interpreting large sets of incomplete and messy data. I found the productive combination of the distinct skill-sets of myself and my experimental collaborators to be immensely satisfying, and I would hope to sustain such a co-operative environment in future work.

        I've presented my work at several conferences, to audiences ranging from statistical physicists to molecular biologists, and have authored and contributed to papers, one of which was selected for the front cover of Physical Review Letters.

        I've had experience using Bioinformatics software to analyse sequence data, using Amazon's cloud computing platform. In my spare time I've a great interest in software development, and have completed several personal projects, which have included building web applications from the ground up. I'm very comfortable using common software development tools such as version control, automating tasks and am capable in Linux and Windows environments. I don't have hands-on experience doing Bayesian analysis or machine learning, but I'm familiar with the theory behind both, and have experimented with machine learning libraries (scikit-learn).

        My doctoral work has been done in a very interdisciplinary environment, and over its course my interests have shifted to a more biological focus; I would be delighted to have an opportunity to continue to use my interests in both science and software to make a real impact on the world.

        \closing{Regards,}

    \end{letter}        

\end{document}

